### 2013-10-02 src2/thesis.tex
apa

%\usepackage{code}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{lingmacros}
\usepackage{subfig}

@@

\newcommand{\thesistitle}{Not decided upon}

@@

\large Bo Joel Svensson
\vfill

\vspace{1cm}
\normalsize
{\sc Department of Computer Science and Engineering}\\
{\sc Chalmers University of Technology and G\"oteborg University}\\
G\"oteborg, Sweden 2013

@@

@@

\newpage

>>>>

%\usepackage{code}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{lingmacros}
\usepackage{subfig}
\usepackage{fancyhdr}

@@

\newcommand{\thesistitle}{Not decided upon}
\newcommand{\dept}{Department of Computer Science and Engineering}
\newcommand{\uni}{Chalmers University of Technology and G\"oteborg University}
\newcommand{\group}{Functional Programming Research Group}

@@

\large Bo Joel Svensson
\vfill
\includegraphics[width=120mm]{./img/ChalmGUtextsvEng}\\[5mm]
\includegraphics[height=4cm]{./img/ChalmGUmarke}\\

\vspace{1cm}
\normalsize
{\sc \dept}\\
{\sc \uni}\\
G\"oteborg, Sweden 2013

@@

% ---------------------------------------------------------------------------
% Tryckortssida
% ---------------------------------------------------------------------------

\quad \vfill

{\noindent\large\bf\thesistitle} \\
\noindent Bo Joel Svensson \\
\noindent ISBN \\

\vspace{1cm}

\noindent\copyright {\sc {Bo Joel Svensson}}, 2013 \\*[5mm]
\vspace{1cm}

\noindent Technical Report ..D\\
\noindent ISSN                \\
\noindent \dept \\
\noindent \group\\

\vspace{1cm}

\noindent \uni \\
\noindent SE--412~96~~G\"oteborg, Sweden\\
\noindent Phone: +46 (0)31--772~1000 \\

\vspace{1cm}

\noindent Printed in Sweden\\
\noindent Chalmers Reproservice\\
\noindent G\"oteborg, Sweden 2013

\thispagestyle{empty}

\clearpage
\pagenumbering{roman}

@@

\pagenumbering{arabic}
\pagestyle{fancy}
\fancyfoot{}
\fancyhead[LO]{}
\fancyhead[RO]{\leftmark}
\renewcommand{\headrulewidth}{0.0pt}
\fancyhead[LE,RO]{\thepage}
